### 2004-05-10 Documentation/part2.tex
*** empty log message ***

\chapter{General Concept}

The aim of AEDL is to describe a large variety of complex experiments
by a limited number of parameters and to allow a representation of
very different setups within one data structure, thus enabling a
universal rate and $\chi^2$ computation. Usually in dealing with
experiment simulations a new piece of code is written and compiled
for each different experiments. In many cases even changes of some
parameter like the number of bins requires the recompilation of
large portions of the source code. This technique may however soon
reach its limits in cases where the simulated experiments are rather complex
and/or more than one kind of experiment is going to examined. Furthermore
is is very difficult to assure the correctness of the results obtained
in this way since every time a new piece of code is added to handle a new
experiment new errors will be introduced.

Thus a general and flexible experiment description language is needed. 
A neutrino experiment can be split into three parts: source, oscillation
and detection. The sources within \GLOBES\ are assumed to be stationary
point sources and each experiment has only one source. Specifically this
does not allow to study cases where the time dependence of the neutrino flux
is of physical significance like \eg\ in supernov\ae. It however is possible
to study beams which have a bunch structure, since the time dependence of the
neutrino source is physically only in as far important as it is used to
suppress backgrounds. Also geometrical effects of a source distribution like
\eg\ in the Sun can not described in this way. For this kind of sources
the oscillation part of an 
experiment is simply
given by the baseline and the matter density profile.

While
it is comparatively simple to define a general neutrino source 
and the oscillation physics, the general properties of a detector are more
complicated. The basic assumption in building an abstract detector description
is \emph{linearity}, \ie\ two neutrino events do not interfere with each other.
Furthermore it is assumed that all information on the oscillation physics 
is given by the \emph{reconstructed} flavour and energy of a 
neutrino event. The term ``reconstructed'' implies that there is not a single
well defined value for each event and variable but a distribution of possible
values. This illustrated in figure~\ref{fig:distro} for the energy variable.
The same is of course possible with the flavour variable. In that case however
only discrete values are possible.
%
\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.6\textwidth]{mapping}
\end{center}
\caption{\label{fig:distro} A detector maps the true values into
a distribution of reconstructed values of a parameter. Here the energy is 
shown.}
\end{figure}
%

This picture also can be formulated in a more mathematical language. Let $x$
be the true variable and $x'$ the reconstructed variable then $f(x)$ is the
distribution of true values and $p(x')$ is the distribution of reconstructed
values. Then the detector function  $D(x,x')$ which describes 
the mapping performed by the detector is defined by
\begin{eqnarray}
\label{eq:mapping}
p(x')&=&\int dx\, f(x)\cdot D(x,x')\,.
\end{eqnarray}
Obviously equation~\ref{eq:mapping} can only describe the detector correctly
when the condition of linearity is fulfilled. Within this model a detector
is completely specified by a set of $D(E,E')$ for the energy variable $E$
and a set $D(F,F')$ for the flavour variable $F$, where usually $D(E,E')$ also
depends on the true flavour $F$ as well as $D(F,F')$ depends on the true energy
$E$. Those sets of mapping functions usually will be obtained by a 
full detector simulation and can be obtained by using as input 
distribution $f(x)$ a delta distribution $\delta(x-x_0)$.

In order to allow a systematic experiment definition including various
sources of systematical errors we use several layers. The first layer is
the so called ``channel'', it is the link between the oscillation physics
and the detector. A channel specifies how a certain neutrino type in the 
source is mapped into a reconstructed neutrino type, \eg\ a muon neutrino
oscillates into an electron neutrino and subsequently interacts via
quasi-elastic charged current scattering. The measured energy and direction of
the electron in the detector finally allow to reconstruct the neutrino energy.
The channels are the building blocks for so called ``rules'' which
contain information like the efficiencies and systematical errors. An example
could look like this: the efficiency for quasi-elastics electron neutrino
events is $0.4$. There is a fraction of $0.01$ of all neutral current events
which are mis-identified as quasi-elastic electron neutrino events. 
The neutral current fraction is only known within $10\%$ and there is
an energy scale uncertainty of $100\,\mathrm{MeV}$. Thus a rule connects the
event rates to the calculation of a $\chi^2$ which properly includes 
systematical errors. This $\chi^2$ is then the starting point for the
oscillation physics analysis.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Getting started}

As a first example we discuss how to define a neutrino factory experiment using
AEDL. The first line of every experiment definition file is
\begin{quote}
{\tt !\%GLoBES}
\end{quote}

We tell \GLOBES\ that we want to use the built-in neutrino factory
flux originating from stored $\mu^+$'s. This is achieved by setting 
the builtin variable to $1$.  Next the energy of the muons is specified
to be $50\,\mathrm{GeV}$ by the parent energy variable. It is assumed
that there will be $5.33\cdot 10^{20}$ useful muon decays per year
and that this luminosity is available for $8$ years.
\begin{quote}
{\tt /* beam */}\\
{\tt flux(\#mu\_plus)<\\
\tb  @builtin = 1\\
\tb  @parent\_energy = 50.0\\
\tb  @stored\_muons = 5.33e+20\\
\tb  @time = 8.0\\
>}\\
\end{quote}
This specific flux can be later on refered to as {\tt \#mu\_plus}.

\begin{quote}
{\tt \$target\_mass = 50}\\
{\tt \$numofbins = 20}\\
{\tt \$emin = 4.0}\\
{\tt \$emax = 50.0}
\end{quote}
The target mass 
is $50\,\mathrm{kt}$ and a total of $ 4.264\cdot10^{21}$
muons is stored. The data is divided into 20 energy bins ranging from
$4\,\mathrm{GeV}$ to $50\,\mathrm{GeV}$.

Next a file has to be specified which contains the cross section we want to 
use.
\begin{quote}
{\tt /* cross section */}\\
{\tt cross(\#CC)<}\\
{\tt \tb @cross\_file = XCC.dat}\\
{\tt >}
\end{quote}
The command {\tt cross} tells the parser that a cross section environment
begins and has the name {\tt \#CC}. These names are used to refer later on
to this specific environment and each name begins with a leading {\tt \#}.
Whenever we need to specify a cross section from here on we can use {\tt \#CC}
to refer to the cross section as given in the file {\tt XCC.dat}.

Of course also the baseline and matter profile have to be specified, which
 looks like this
\begin{quote}
{\tt /* baseline */}\\
{\tt \$baseline = 3000.0}\\
{\tt \$densitytab = \{3.5\}}\\
{\tt \$lengthtab = \{3000.0\}}\\
{\tt \$density\_error = 0.05}
\end{quote}
The curly brackets used for the definition of {\tt \$densitytab} and
{\tt \$lengthtab} delimit as simple list of numbers -- here the lists
have length $1$. {\tt \$density\_error} is the relative $1\,\sigma$ uncertainty
on the density.

The energy resolution function can easily be specified with
\begin{quote}
{\tt /* energy resolution */}\\
{\tt energy(\#MINOS)<}\\
{\tt \tb @type = 1}\\
{\tt \tb @sigma\_e = \{0.15,0.0,0.0\}}\\
{\tt >}
\end{quote}
The {\tt energy} command opens the corresponding energy environment and
the energy resolution function defined here is refered to by the name 
{\tt \#MINOS}. Out of several possibilities it employs algorithm $1$,
the simplest and fastest one. The actual energy resolution is specified
by the energy resolution variable which is a list of three elements. Each 
element is one parameter of a general resolution function as defined in 
equation ~\ref{eq:sigma_e}.

Now we define the one appearance and the corresponding disappearance 
channel of a neutrino factory: 
$\nu_e\rightarrow\nu_\mu$  and $\bar\nu_\mu\rightarrow\bar\nu_\mu$ 
($\mu^+$ stored).
\begin{quote}
{\tt /* channels */}\\
{\tt channel(\#appearance)<}\\
{\tt \tb @channel = \#mu\_plus: +: electron: muon: \#CC: \#MINOS}\\
{\tt >}\\
{\tt channel(\#disappearance)<}\\
{\tt \tb @channel = \#mu\_plus: -: muon: muon: \#CC: \#MINOS}\\
{\tt >}
\end{quote}
The first element is the name of the flux as defined previously, here we use
the flux named {\tt \#mu\_plus}. The second element $\pm$ determines whether 
neutrinos or anti-neutrinos are
taken from the flux table. The third position defines the initial flavour
and the forth position the final flavour, followed by the name of the cross
section and energy resolution function.

The last step is to assemble the channels into a rule.
\begin{quote}
{\tt /* rules */}\\
{\tt rule(\#rule1)<}\\
{\tt \tb @signal = 0.45 @ \#appearance}\\
{\tt \tb @signalerror = 0.001 : 0.0001}\\
{\tt \tb @background = 1.0e-05 @ \#disappearance}\\
{\tt \tb @backgroundcenter = 1 : 0.0}\\
{\tt \tb @backgrounderror = 0.05 : 0.0001}\\
{\tt \tb @errordim = 0}\\
{\tt \tb @energy\_window = 4.0 : 50.0}\\
{\tt >}
\end{quote}
The signal variable says that the signal in our experiment is the 
channel named {\tt \#appearance} with an constant efficiency of $0.45$.
The signal error variable has two components: the first one is the
normalization error of the signal, here it is $0.1\%$. The second component
signifies the energy calibration error of the signal, whose definition 
can be found in section~\ref{sec:energy}. The background variable
specifies the composition of the beam background and this case is
given by the channel named {\tt \#disappearance}, \ie\ this are
the muons whose charge has been mis-identified. They enter the calculation
with an efficiency of $1\cdot 10^{-5}$. The background center variable allows
to rescale the total background contribution which is especially useful if
there are many background components. 
The background error variable is defined in the same way as the signal error
variable, \ie\ we have a $5\%$ background uncertainty.
The error dimension variable selects how
the systematical errors are treated according to table~\ref{tab:error_dim}.

The above defined experiment represents a first version of a neutrino factory
experiment. It still lacks the correct energy dependence of the efficiencies
and of course the channels and rules for the operation with $\mu^-$ stored

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Features of the  AEDL}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Syntax and types of  AEDL}
\label{sec:syntax}

@@

One nasty thing is that a line feed character \verb+\n+ is necessary at
 the end of input, alternatively you can put a comment at the end.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Source properties}
\label{sec:source}

>>>>

\chapter{Getting started}

Here the general concept of the AEDL is described and illustrated by an example. In addition, a short introduction to the syntax of the AEDL is given.

\section{General concept of the experiment simulation}

The goal of AEDL is to describe a large number of complex and very 
different experiments by a limited number of parameters. It allows a
representation of very different setups within one data structure, and thus implements universal rate and $\chi^2$ computation methods. For experiment simulations, a new piece of code is usually written and compiled
for each different experiment. In many cases, even parameter changes, such as
the number of bins, requires the recompilation of the source code. 
However, such a technique soon reaches its limits when the simulated experiments are rather complex, or more than one type of experiment is studied simultaneously. Furthermore, it is very difficult to verify the correctness of the obtained results, since every time a new piece of code is added to 
deal with a new experiment type, new errors will be introduced.

Thus, a general and flexible experiment description language is needed.  
The description of a neutrino experiment can be split into three parts: Source, oscillation, and detection. The neutrino sources within \GLOBES\ 
are assumed to be stationary point sources, where each experiment has only 
one source. This restricts the classes of neutrino sources which can be studied with \GLOBES :
\begin{itemize}
\item
 Experiments using many point-like sources can only be approximated. One example are reactor experiments using many distant reactor blocks.
\item
 Geometrical effects of a source distribution, such as in the sun or the atmosphere, can not be described.
\item
 Sources with a physically significant time dependencies  can not be studied, such as  supernov\ae. It is, however, possible
to study beams with bunch structure, since the time dependence of the
neutrino source is physically only important to suppress backgrounds. 
\end{itemize}

The description of the neutrino oscillation physics is, at least numerically, relatively simple. We use the {\em evolution operator method} to compute the neutrino oscillation probabilities and divide the matter density profile into layers with constant matter densities. For each of these layers, the Hamiltonian in matter is diagonalized in order to propagate the neutrino transition amplitudes. Finally, the transition probability is obtained by the absolute square of the total neutrino transition amplitudes. Depending on the precision of the studied experiment, this approach turns out to be precise enough in Earth matter even for a small number matter density steps. Since we allow an uncertainty of the matter density profile, it is, in fact, in most cases sufficient to consider only one density step with the average matter density together with a matter density uncertainty~\cite{Ohlsson:2003ip}. Note that this approach may not be applicable to quickly varying extraterrestrial matter density profiles.

While it is comparatively simple to define a general neutrino source 
and to compute the oscillation physics, the general properties of a detector simulation are much more complicated. The basic assumption in building an abstract detector description is \emph{linearity}, \ie , that two neutrino events do not interfere with each other. Furthermore it is assumed that all information on the oscillation physics 
is given by the \emph{reconstructed} flavor and energy of a 
neutrino event. The term ``reconstructed'' implies that the well-defined energy of the incident neutrino, which can not be directly observed, translates via secondary particles and the detection properties into a distribution of possible energy values. This process is illustrated in \figu{distro} for the energy variable. 
%
\begin{figure}[ht]
\begin{center}
\includegraphics[width=0.6\textwidth]{mapping}
\end{center}
\caption{\label{fig:distro} A detector maps a true parameter value onto
a distribution of reconstructed parameter values. This is illustrated here for there energy.}
\end{figure}
% 
The same, in principle, applies to the nature of the neutrino flavor. However, in this case only discrete values are applicable. Note that the reconstructed neutrino energy and the neutrino flavor are the only observables in \GLOBES .

This picture can also be formulated in a more mathematical way. Let us define $x$ as the true parameter value and $x'$ as the reconstructed parameter value. Similarly, $f(x)$ is the distribution of true parameters values and $p(x')$ is the distribution of reconstructed parameter values. Then the detector function  $D(x,x')$, which describes the mapping performed by the detector, is given by
\begin{eqnarray}
\label{equ:mapping}
p(x')&=&\int dx\, f(x)\cdot D(x,x')\,.
\end{eqnarray}
Obviously \equ{mapping} only describes the detector properly
if the linearity condition is fulfilled. Within this model, a detector
is completely specified by a set of $D(E,E')$ for the energy variable $E$,
and a set $D(F,F')$ for the flavor variable $F$. In general, $D(E,E')$ also depends on the true flavor $F$, as well as $D(F,F')$ depends on the true energy $E$. These sets of mapping functions usually are obtained from a 
full detector simulation and can be obtained by using as input 
distribution $f(x)$ a delta distribution $\delta(x-x_0)$.

In order to implement a experiment definition including various
sources of systematical errors, we use several abstraction levels. 
The first level is the so-called ``channel'', which is the link between 
the oscillation physics and the detection properties for a specfific oscillation pattern. A channel specifies the mapping of a specific neutrino flavor produced by the source onto a reconstructed neutrino flavor.
For example, a muon neutrino oscillates into an electron neutrino and subsequently interacts via quasi-elastic charged current scattering. The measured energy and direction of
the secondary electron in the detector then allows to reconstruct the neutrino energy. The connection from the source flux of the muon neutrino, via the  probability to appear as a electron neutrino, to its detection properties (such as cross sections and energy smearing) is encapsulated into the channel.

The channels are the building blocks for the so-called ``rules''. In general, a rule consists of one or more ``signal'' and ``background'' oscillation channels, which are normalized with efficiencies. The event numbers from these channels are added {\em before} the $\chi^2$-value is calculated. In addition, each rule implements an {\em independent} systematics, such as signal and background normalization errors. Eventually, each rule gives a $\chi^2$-value, and the total $\chi^2$ is obtained by adding the $\chi^2$'s of all rules. 
 An example for a rule could look like this: We want to detect electron neutrino appearance (``signal''), where the overall efficiency for quasi-elastics electron neutrino events is $0.4$. There is a fraction of $0.01$ of all neutral current events which are mis-identified as quasi-elastic electron neutrino events (``background''). The neutral current fraction is only known within $10\%$ (``background uncertainty'') and there is
an energy scale uncertainty of $100\,\mathrm{MeV}$ (``energy calibration error'').
All this systematics is independent of the other rules.  Thus, a rule connects the event rates to the calculation of a $\chi^2$ which properly includes 
systematical errors. The resulting $\chi^2$ is then the starting point for the
oscillation physics analysis. Note again that
\begin{itemize}
\item
 Within each rule the event numbers are added.
\item
 Within each rule the systematics is treated independently from the other rules.
\item
 For each rule the $\chi^2$ is computed; the $\chi^2$'s from all rules are added.
\end{itemize}

Of course, an abstract experiment definition language can not simulate all possible types of experiments. As we have seen, there are several assumptions for source and detector. However, it turns out that \GLOBES\ can be applied to a large number of experiment types, such as conventional beams, superbeams, neutrino factories, $\beta$-Beams, and reactor experiments.

\section{A simple example for the AEDL}

Experiments are in \GLOBES\ defined by the Abstract Experiment Definition Language (AEDL). The experiment definition is written into a text file using the AEDL syntax. Currently, a number of pre-defined experiment definition files are provided with \GLOBES , which have to be modified manually in order to define new experiments. An IDE (Integrated Developement Environment) for AEDL files is currently in preparation. The application software then uses this text file to initialize the experiment, where other secondary files might read for source fluxes, cross sections \etc . In this section, we show the definition of a very simple neutrino factory in AEDL, where we do not go into details. In the next chapter, we will discuss each of the individual steps in detail.

The first line of every experiment definition file has to be
\begin{quote}
{\tt !\%GLoBES}
\end{quote}
in order not to confuse it with some other file format.
%
First, we instruct \GLOBES\ to use the built-in source flux for a neutrino factory
originating from stored $\mu^+$'s. Therefore, we set the {\tt @builtin} variable to $1$. Next, we specify the muon energy to be $50\,\mathrm{GeV}$ by the {\tt @parent\_energy} variable. We assume 
that there will be $5.33\cdot 10^{20}$ useful muon decays per year
and that this luminosity is available for $8$ years, \ie , a total number
of $ 4.264\cdot10^{21}$ muons is stored:
\begin{quote}
{\tt /* beam */}\\
{\tt flux(\#mu\_plus)<\\
\tb  @builtin = 1\\
\tb  @parent\_energy = 50.0\\
\tb  @stored\_muons = 5.33e+20\\
\tb  @time = 8.0\\
>}\\
\end{quote}
Note that we tell \GLOBES\ that we want to refer to this neutrino source later as as {\tt \#mu\_plus}. 
%
Let us now define a very simple detector with a target mass 
of $50\,\mathrm{kt}$ and $20$ energy bins between
$4\,\mathrm{GeV}$ and $50\,\mathrm{GeV}$: 
\begin{quote}
{\tt \$target\_mass = 50}\\
{\tt \$numofbins = 20}\\
{\tt \$emin = 4.0}\\
{\tt \$emax = 50.0}
\end{quote}
Then we specify the file which contains the cross sections we want to 
use:
\begin{quote}
{\tt /* cross section */}\\
{\tt cross(\#CC)<}\\
{\tt \tb @cross\_file = XCC.dat}\\
{\tt >}
\end{quote}
The command {\tt cross} tells the parser that a cross section environment
begins. It has the name {\tt \#CC}, which can later be used to refer 
to this specific environment, and thus to the file {\tt XCC.dat}. Note that each name begins with a leading {\tt \#}.
%
Of course, the baseline and matter profile have to be specified, too:
\begin{quote}
{\tt /* baseline */}\\
{\tt \$baseline = 3000.0}\\
{\tt \$densitytab = \{3.5\}}\\
{\tt \$lengthtab = \{3000.0\}}\\
{\tt \$density\_error = 0.05}
\end{quote}
The curly brackets used for the definition of {\tt \$densitytab} and
{\tt \$lengthtab} refer to a list of numbers. Here, the lists contain only
one element, because we only use one density layer: We initialize a baseline length of $3000 \, \mathrm{km}$ with a constant matter density of $3.5 \, \mathrm{g/cm^3}$ and a matter density uncertainty of $5\%$ ($1 \sigma$ relative error). Note that the elements in {\tt \$lengthtab} have to add up to the baseline length. 
%
As another ingredient, we have to define the energy resolution function:
\begin{quote}
{\tt /* energy resolution */}\\
{\tt energy(\#MINOS)<}\\
{\tt \tb @type = 1}\\
{\tt \tb @sigma\_e = \{0.15,0.0,0.0\}}\\
{\tt >}
\end{quote}
The {\tt energy} command opens the energy environmen, which has the name 
{\tt \#MINOS} here. Out of several possibilities, it uses algorithm one,
the simplest and fastest one. The actual energy resolution is specified
by the energy resolution variable, which is a list of three elements. Each 
element is one parameter of the general resolution function as defined in 
\eq~\ref{eq:sigma_e}.
%
Now we have all pieces to be able to define the appearance and the corresponding disappearance channel of a neutrino factory: 
$\nu_e\rightarrow\nu_\mu$  and $\bar\nu_\mu\rightarrow\bar\nu_\mu$ 
($\mu^+$ stored).
\begin{quote}
{\tt /* channels */}\\
{\tt channel(\#appearance)<}\\
{\tt \tb @channel = \#mu\_plus: +: electron: muon: \#CC: \#MINOS}\\
{\tt >}\\
{\tt channel(\#disappearance)<}\\
{\tt \tb @channel = \#mu\_plus: -: muon: muon: \#CC: \#MINOS}\\
{\tt >}
\end{quote}
The first element is the name of the flux, which we have already defined above as defined above. The second element $\pm$ determines whether 
neutrinos or anti-neutrinos are taken from the flux table (two different polarities allowed). The third position defines the initial flavor,
and the forth position the final flavor, followed by the name of the cross
section and energy resolution function as defined before.
%
The last step is to encapsulate the channels into a rule:
\begin{quote}
{\tt /* rules */}\\
{\tt rule(\#rule1)<}\\
{\tt \tb @signal = 0.45 @ \#appearance}\\
{\tt \tb @signalerror = 0.001 : 0.0001}\\
{\tt \tb @background = 1.0e-05 @ \#disappearance}\\
{\tt \tb @backgroundcenter = 1 : 0.0}\\
{\tt \tb @backgrounderror = 0.05 : 0.0001}\\
{\tt \tb @errordim = 0}\\
{\tt \tb @energy\_window = 4.0 : 50.0}\\
{\tt >}
\end{quote}
The {\tt @signal} refers to the ``signal'' in our experiment. We use the
above defined channel named {\tt \#appearance} with an constant overall
efficiency of $0.45$. The signal error variable has two components: 
The first one is the normalization error of the signal, here $0.1\%$. The second 
one refers to the energy calibration error of the signal, which is defined 
in \Sec~\ref{sec:energy}. The background variable
specifies the composition of the beam background. In this (simplified) case, we
use the fraction $1\cdot 10^{-5}$ of the channel named {\tt \#disappearance}, \ie , the muon neutrinos with a mis-identified charge. The background center variable allows to rescale the total background contribution from all background components
simultaneously. It is only useful if there is more than one background component, otherwise it is usually $1$. The background error variable is defined such as the signal error variable, \ie\ we have a $5\%$ background uncertainty and a very small energy calibration error. The ``error dimension variable'' {\tt @errordim} selects how the systematical errors are treated (\cf, \Tab~\ref{tab:error_dim}).

The here defined experiment represents a first simplified version of a neutrino factory experiment. It still lacks the correct energy dependence of the efficiencies, the antineutrino disappearance channel, and the channels and rules for the symmetric operation with $\mu^-$ stored. However, it may serve as a simple, introductory example. In the next chapter, we will demonstrate that the AEDL is much more powerful than illustrated here.

% continue here (WW):

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction to the syntax of AEDL}
\label{sec:syntax}

@@

One nasty thing is that a line feed character \verb+\n+ is necessary at
 the end of input, alternatively you can put a comment at the end.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Experiment definition with AEDL}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Source properties}
\label{sec:source}
